IPv6 over Low-Power Wireless Personal Area Networks\\ MSc. Thesis Proposal

### 2009-12-20 trunk/doc/msc-proposal/msc-proposal.tex
proposal: routing requirements

%%
%	Transmission of IPv6 Packets
%%
\chapter{Transmission of IPv6 Packets over 802.15.4}\label{ch:6lowpan}
A low-power wireless personal area network (LoWPAN) is a simple low throughput wireless network comprising low cost and low power devices that conform to the IEEE 802.15.4-2003 standard. The IEEE 802.15.4-2003 standard specifies node-to-node frame delivery between the devices which are within reachable distance from each other. On top of IEEE 802.15.4 a network layer (layer 3 of the seven-layer OSI model) has to be defined that would provide end-to-end packet delivery including routing through intermediate hosts.

@@

\nocite{ieee802.15.4} 
\nocite{eui64} 
\nocite{rfc780}
\nocite{rfc2460}
\nocite{rfc2464}
\nocite{rfc2474}
\nocite{rfc3168}
\nocite{rfc3775}
\nocite{rfc4191}
\nocite{rfc4291} 
\nocite{rfc4443}
\nocite{rfc4861}
\nocite{rfc4862}
\nocite{rfc4919}
\nocite{rfc4944} 
\nocite{draft-usecases-05} 
\nocite{draft-hc-06} 
\nocite{draft-nd-07}

>>>>

%%
%	Transmission of IPv6 Packets
%%
\chapter{Transmission of IPv6 Packets over 802.15.4}\label{ch:6lowpan}
As described in Chapter \ref{ch:ieee802.15.4}, the IEEE 802.15.4-2003 standard specifies the physical layer and media access control for low-rate wireless personal area network providing node-to-node frame delivery between the devices within reachable distance from each other. On top of IEEE 802.15.4 a network layer (layer 3 of the seven-layer OSI model) has to be defined that would provide end-to-end packet delivery including routing through intermediate hosts.

@@

\nocite{ieee802.15.4} 
\nocite{eui64} 
\nocite{rfc780}
\nocite{rfc2460}
\nocite{rfc2464}
\nocite{rfc2474}
\nocite{rfc3168}
\nocite{rfc3775}
\nocite{rfc4191}
\nocite{rfc4291} 
\nocite{rfc4443}
\nocite{rfc4861}
\nocite{rfc4862}
\nocite{rfc4919}
\nocite{rfc4944} 
\nocite{draft-usecases-05} 
\nocite{draft-hc-06} 
\nocite{draft-nd-07}
\nocite{draft-routing-04}
\nocite{draft-protocols-07}
\nocite{draft-rpl-04}
\nocite{draft-routing-metrics-04}
